### 2017-10-25 Paper_v6.tex
adding v6

\usepackage{algorithm2e}
\usepackage{algpseudocode}
%\usepackage[space]{cite}
\urlstyle{rm}

@@

Meta-heuristics like Genetic Algorithms (GAs) \cite{goldberg2006genetic}, Simulated Annealing (SA) \cite{kirkpatrick1983optimization},
Evolutionary Programming \cite{fogel2009artificial} and Differential Evolution (DE) \cite{storn1997differential,tsai2005evolutionary,wang2001hybrid,noman2007inferring} have all shown promise on non-linear multi-modal problems \cite{sun2012parameter}.
These techniques do not make any assumptions, nor do they require, \textit{a~priori} information about the structure of the objective function.
Meta-heuristics are often very effective at finding globally optimal or near optimal solutions.
For example, Mendes et al. used SA to estimate rate constants for the inhibition of HIV proteinase \cite{mendes1998non},
while Modchang et al. used a GA to estimate parameters for a model of G-protein-coupled receptor (GPCR) activity \cite{modchang2008mathematical}.
Parameter estimates obtained using the GA stratified the effectiveness of two G-protein agonists, N6-cyclopentyladenosine (CPA) and 5'-N-ethylcarboxamidoadenosine (NECA).
Tashkova et al. compared different meta-heuristics for parameter estimation on a dynamic model of endocytosis;
DE was the most effective of the approaches tested \cite{tashkova2011parameter}.
Banga and co-workers have also successfully applied scatter-search to estimate model parameters \cite{villaverde2012cooperative,rodriguez2006novel,egea2007scatter}.
Hybrid approaches, which combine meta-heuristics with local optimization techniques, have also become popular.
For example, Villaverde et al. developed the enhanced scatter search (eSS) method \cite{egea2010evolutionary}, which combined scatter and local search methods,
for parameter estimation in biological models \cite{villaverde2015biopredyn}.
However, despite these successes, a major drawback of most meta-heuristics remains the large number of function evaluations required to explore parameter space.
Performing numerous potentially expensive function evaluations is not desirable (and perhaps not feasible) for many types of biochemical models.
Alternatively, Tolson and Shoemaker found, using high-dimensional watershed models, that perturbing only a subset of parameters was an effective strategy for estimating
parameters in expensive models \cite{tolson2007dynamically}. Their approach, called Dynamically Dimensioned Search (DDS),
is a simple stochastic single-solution heuristic that estimates nearly optimal solutions within a specified maximum number of function (or model) evaluations.
Thus, while meta-heuristics are often effective at estimating globally optimal or nearly optimal solutions, they require a large number of function evaluations to
converge to a solution.

@@

Villaverde and co-workers published a set of benchmark biochemical problems to evaluate parameter estimation methods \cite{villaverde2015biopredyn}.
They ranked the example problems by computational cost from most to least expensive.
We evaluated the performance of DOPS on problems from the least and most expensive categories.
The least expensive problem (henceforth referred to as CHO model) was a metabolic model of Chinese Hamster Ovary (CHO) with 35 metabolites, 32 reactions and 117 parameters \cite{villaverde2014high}.
The biochemical reactions were modeled using modular rate laws and generalized Michaelis-Menten kinetics.
On the other hand, the expensive problem was a genome scale kinetic model of \textit{Saccharomyces~cerevisiae} with 261 reactions, 262 variables and 1759 parameters \cite{smallbone2013large} (henceforth referred to as yeast model).
In both cases, synthetic time series data generated with known parameter values, was used to estimate model parameters.
For yeast model, the time series data consisted of 44 observables, and for problem B4 the data corresponded to 13 different metabolite measurement sets.
We fixed the number of function evaluations at $\mathcal{N}$ = 4000, and trained both models against the synthetic experimental data.
DOPS produced good fits to the synthetic data (Fig. \ref{fig-sims-b1} and Fig. \ref{fig-sims-b4}), and recapitulated the nominal parameter values using only $\mathcal{N}\leq~4000$ function evaluations (Fig. \ref{fig-benchmark}).
On the other hand, enhanced scatter search (eSS) with a local optimizer took on order $10^{5}$ function evaluations for the same problems.
Thus, DOPS estimated the parameters in benchmark biochemical models, and recovered the original parameters from synthetic data, using fewer function evaluations.
Next, we compared the performance of DOPS with the four other meta-heuristics for a model of the human coagulation cascade.

@@

\subsection*{Dynamic optimization with particle swarms (DOPS).}
DOPS is a novel meta-heuristic which combines multi-swarm particle swarm optimization
with the dynamically dimensioned search (Fig. \ref{fig-algorithm}) and (Algo. \ref{algo_ddspso}).  Particle swarm optimization is an evolutionary algorithm that uses a population of particles (solutions) to find an optimal solution.
Each particle is updated based on its on experience (particle best) and the experience of all other particles within the swarm (global best) \cite{clerc2010particle}\cite{blondin2009particle}\cite{abraham2006swarm}.   
Multi-swarm particle swarm optimization is a variant of particle swarm optimization that uses multiple swarms instead of a single swarm.
DOPS uses a novel update rule of particles within each swarm. This rule uses only particle positions but not particle velocities in the update rule. This differs from existing PSO methods that rely both on particle position and velocity for update. 
The update rule further described in detail in the methods.
The goal of DOPS is to estimate optimal or near optimal parameter vectors for high-dimensional biological models within a specified number of function evaluations.
Toward this objective, DOPS begins by using a particle swarm search and then dynamically switches, using an adaptive switching criteria, to a DDS search phase.
Dynamically Dimensioned Search (DDS) is a single solution based search algorithm. It was developed by Tolson and Shoemaker to obtain good solutions to high-dimensional search problems within a fixed number of function evaluations. 
DDS starts as a global search algorithm by perturbing all the dimensions. Later the number of dimensions that are perturbed is decreased with a certain probability. 
The probability that a certain dimension is perturbed reduces (a minimum of one dimension is always perturbed) as the iterations increase. 
This causes the algorithm to behave as a local search algorithm as the number of iterations increase.
The perturbation magnitude of each dimension is from normal distribution with zero mean. The standard deviation that was used in the original DDS paper and the current study is 0.2.
DDS performs a greedy search where the solution is updated only if it is better than the previous solution.
The combination of perturbing a subset of dimensions along with greedy search indirectly relies on model sensitivity to a specific parameter combination. 
For the sake of brevity we are not providing the entire pseudo code of DDS here. The reader is requested to refer to Figure 1 of the original paper by Tolson and Shoemaker \cite{tolson2007dynamically}.

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{A randomized swarm of particles of size $NP\times K$ and fixed number of function evaluations N}
\Output{Optimized parameter vector of size $1\times K$ }
\BlankLine
\emph{Initialize the particles randomly and assign particles randomly to $k$ sub-swarms}\;
\While{$j\leq N$}{

\If{mod(j,G)=0} {
 \emph{Reassign particles to $k$ sub-swarms}\;
}

@@

\subsubsection*{Phase 2: DDS phase.}

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{Candidate vector $\mathcal{G}$ from swarm search and $\left(1-\mathcal{F}\right)*\mathcal{N}$ evaluations}
\Output{Optimized parameter vector of size $1\times K$ }
\BlankLine
\While{$j\leq \left(1-\mathcal{F}\right)*\mathcal{N}$}{

\emph{Assign probability of perturbation to each dimension $\mathcal{P}_{i}$ according to equation 7}\;
\emph{Select a subset of dimensions based on a threshold value for perturbation}\;
\emph{Update candidate solution $\mathcal{G}({J})$  according to equation 5}\;
\emph{Ensure updated solution $\mathcal{G}_{new}({J})$ is within bounds using Algorithm 2}\;

}
\caption{Pseudo code for the Dynamically Dimensioned Search (DDS) method.}\label{algo_dds}
\end{algorithm}\DecMargin{1em}

@@

\begin{table}[h]
\centering
\caption{Table with optimization settings and results for the coagulation problem, the benchmarks and test functions using DOPS. For each problem the bounds on the parameter vector, the total number of function evaluations, the best initial objective value and the best final objective value are specified. Here $pnom$ indicates the nominal or true parameter vector of the model. Nominal objective value represents the objective value using the true parameter vector or the nominal parameter vector. The CPU time is the time taken for the problem on a 2.4GHz Intel Xeon Architecture running Matlab 2014b.}
\label{table:benchmark-problems}
\resizebox{\columnwidth}{!}{
\begin{tabular}{r|lllll}
\hline\\
                        & Coagulation 					& Yeast model          	& CHO model          & Ackley 			& Rastrigin \\\\
\hline\\
Evaluations   					& 4000                  & 4000         	& 4000        & 4000        & 4000        \\
Lower Bound             & 0.001.pnom            & 5.pnom       	& 5.pnom      & 30          & 5.12        \\
Upper Bound             & 1000.pnom             & 0.2.pnom     	& 0.2.pnom    & -15         & -5.12       \\
CPU Time                & 10.1 hrs         			& 38.3 hrs 			& 6.2 min 		& 2.8 s 			& 2.6 s    		\\\\

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure_4_Errors_convergence_v2.pdf}
\caption{Error convergence rates of the five different algorithms on the coagulation model. The objective error is the mean over $\mathcal{T}$= 25 trials.
DOPS, DDS and SA have the steepest drop in error during first 300 function evaluations. Thereafter the error drop in DDS and SA remains nearly constant whereas DOPS continues to drops further.
At the end of 4000 function evaluations DOPS attains the lowest error. The next best estimate using DDS is nearly three times greater than the lowest error using DDS.
}\label{fig-convergence}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S1_B1_sims.pdf}
\caption{\textbf {(Data fits for Yeast Model (B1))} Pseudo-experimental data (red circles) vs. optimal solution obtained using DOPS (solid blue lines) for the 44 observed states. X axis: time [s]; Y axis: metabolite concentrations [mM].
}\label{fig-sims-b1}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S2_B4_sims.pdf}
\caption{\textbf {(Data fits for CHO Model (B4))} Pseudo-experimental data (red x) vs. optimal solution obtained using DOPS (solid blue lines) for the 13 observed states. X axis: time [s]; Y axis: metabolite concentrations [mM].
}\label{fig-sims-b4}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S3_B1_B4_params_measuredstates.pdf}
\caption{ \textbf {(A)} Difference between nominal and optimal parameters for problem B1: Genome wide kinetic model of \textit{S.cerevisiae} with 1759 unknown parameters. \textbf {(B)} Difference between experimental (measured) data and data simulated with optimal parameters for yeast model: Genome wide kinetic model of \textit{S.cerevisiae} with 1759 unknown parameters. \textbf {(C)} Difference between nominal and optimal parameters for problem B4: Metabolic model of Chinese  Hamster Ovary Cells (CHO) cells with 117 parameters. \textbf {(D)} Difference between experimental (measured) data and data simulated with optimal parameters for CHO model: Metabolic model of Chinese  Hamster Ovary Cells (CHO) cells with 117 parameters.
}\label{fig-benchmark}
\end{figure}

>>>>

\usepackage{algorithm2e}
\usepackage{algpseudocode}
\usepackage{subfig}
%\usepackage[space]{cite}
\urlstyle{rm}

@@

Meta-heuristics like Genetic Algorithms (GAs) \cite{goldberg2006genetic}, Simulated Annealing (SA) \cite{kirkpatrick1983optimization},
Evolutionary Programming \cite{fogel2009artificial} and Differential Evolution (DE) \cite{storn1997differential,tsai2005evolutionary,wang2001hybrid,noman2007inferring} have all shown promise on non-linear multi-modal problems \cite{sun2012parameter}.
These techniques do not make any assumptions, nor do they require, \textit{a~priori} information about the structure of the objective function.
Meta-heuristics are often very effective at finding globally optimal or near optimal solutions.
For example, Mendes et al. used SA to estimate rate constants for the inhibition of HIV proteinase \cite{mendes1998non},
while Modchang et al. used a GA to estimate parameters for a model of G-protein-coupled receptor (GPCR) activity \cite{modchang2008mathematical}.
Parameter estimates obtained using the GA stratified the effectiveness of two G-protein agonists, N6-cyclopentyladenosine (CPA) and 5'-N-ethylcarboxamidoadenosine (NECA).
Tashkova et al. compared different meta-heuristics for parameter estimation on a dynamic model of endocytosis;
DE was the most effective of the approaches tested \cite{tashkova2011parameter}.
Banga and co-workers have also successfully applied scatter-search to estimate model parameters \cite{villaverde2012cooperative,rodriguez2006novel,egea2007scatter}.
Hybrid approaches, which combine meta-heuristics with local optimization techniques, have also become popular.
For example, Villaverde et al. developed the enhanced scatter search (eSS) method \cite{villaverde2015biopredyn}, which combined scatter and local search methods,
for parameter estimation in biological models  \cite{egea2007scatter}.
However, despite these successes, a major drawback of most meta-heuristics remains the large number of function evaluations required to explore parameter space.
Performing numerous potentially expensive function evaluations is not desirable (and perhaps not feasible) for many types of biochemical models.
Alternatively, Tolson and Shoemaker found, using high-dimensional watershed models, that perturbing only a subset of parameters was an effective strategy for estimating
parameters in expensive models \cite{tolson2007dynamically}. Their approach, called Dynamically Dimensioned Search (DDS),
is a simple stochastic single-solution heuristic that estimates nearly optimal solutions within a specified maximum number of function (or model) evaluations.
Thus, while meta-heuristics are often effective at estimating globally optimal or nearly optimal solutions, they require a large number of function evaluations to
converge to a solution.

@@

Villaverde and co-workers published a set of benchmark biochemical problems to evaluate parameter estimation methods \cite{villaverde2015biopredyn}.
They ranked the example problems by computational cost from most to least expensive.
We evaluated the performance of DOPS on problems from the least and most expensive categories.
The least expensive problem (henceforth referred to as problem B4) was a metabolic model of Chinese Hamster Ovary (CHO) with 35 metabolites, 32 reactions and 117 parameters \cite{villaverde2014high}.
The biochemical reactions were modeled using modular rate laws and generalized Michaelis-Menten kinetics.
On the other hand, the expensive problem was a genome scale kinetic model of \textit{Saccharomyces~cerevisiae} with 261 reactions, 262 variables and 1759 parameters \cite{smallbone2013large} (henceforth referred to as problem B1).
In both cases, synthetic time series data generated with known parameter values, was used to estimate model parameters.
For problem B1, the time series data consisted of 44 observables, and for problem B4 the data corresponded to 13 different metabolite measurement sets.
We fixed the number of function evaluations at $\mathcal{N}$ = 4000, and trained both models against the synthetic experimental data.
DOPS produced good fits to the synthetic data (Fig. \ref{fig-sims-b1} and Fig. \ref{fig-sims-b4}), and recapitulated the nominal parameter values using only $\mathcal{N}\leq~4000$ function evaluations (Fig. \ref{fig-benchmark}).
On the other hand, enhanced scatter search (eSS) with a local optimizer took on order $10^{5}$ function evaluations for the same problems.
Thus, DOPS estimated the parameters in benchmark biochemical models, and recovered the original parameters from synthetic data, using fewer function evaluations.
Next, we compared the performance of DOPS with the four other meta-heuristics for a model of the human coagulation cascade.

@@

\subsection*{Dynamic optimization with particle swarms (DOPS).}
DOPS is a novel meta-heuristic which combines multi-swarm particle swarm optimization
with the dynamically dimensioned search (Fig. \ref{fig-algorithm}) and (Algo. \ref{algo_ddspso}).
The goal of DOPS is to estimate optimal or near optimal parameter vectors for high-dimensional biological models within a specified number of function evaluations.
Toward this objective, DOPS begins by using a particle swarm search and then dynamically switches, using an adaptive switching criteria, to a DDS search phase.

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
\Input{A randomized swarm of particles of size $NP\times K$ and fixed number of function evaluations N}
\Output{Optimized parameter vector of size $1\times K$ }
\BlankLine
\emph{Initialize the particles randomly and assign particles randomly to various sub-swarms}\;
\While{$j\leq N$}{

\If{mod(j,G)=0} {
 \emph{Reassign particles to different sub-swarms}\;
}

@@

\subsubsection*{Phase 2: DDS phase.}
Dynamically Dimensioned Search (DDS) is a single solution based search algorithm. DDS is used to obtain good solutions to high-dimensional search problems within a fixed number of function evaluations. DDS starts as a global search algorithm by perturbing all the dimensions. Later the number of dimensions that are perturbed is decreased with a certain probability. The probability that a certain dimension is perturbed reduces (a minimum of one dimension is always perturbed) as the iterations increase. This causes the algorithm to behave as a local search algorithm as the number of iterations increase. The perturbation magnitude of each dimension is from normal distribution with zero mean. The standard deviation that was used in the original DDS paper and the current study is 0.2.
DDS performs a greedy search where the solution is updated only if it is better than the previous solution. The combination of perturbing a subset of dimensions along with greedy search indirectly relies on model sensitivity to a specific parameter combination. The reader is requested to refer to the original paper by Tolson and Shoemaker for further detail \cite{tolson2007dynamically}.

@@

\begin{table}[h]
\centering
\caption{Table with optimization settings and results for the coagulation problem, the benchmarks and test functions using DOPS. For each problem the bounds on the parameter vector, the total number of function evaluations, the best initial objective value and the best final objective value are specified. Here $pnom$ indicates the nominal or true parameter vector of the model. Nominal objective value represents the objective value using the true parameter vector or the nominal parameter vector. The CPU time is the time taken for the problem on a 2.4GHz Intel Xeon Architecture running Matlab 2014b.}
\label{table:benchmark-problems}
\resizebox{\columnwidth}{!}{
\begin{tabular}{r|lllll}
\hline\\
                        & Coagulation 					& B1           	& B4          & Ackley 			& Rastrigin \\\\
\hline\\
Evaluations   					& 4000                  & 4000         	& 4000        & 4000        & 4000        \\
Lower Bound             & 0.001.pnom            & 5.pnom       	& 5.pnom      & 30          & 5.12        \\
Upper Bound             & 1000.pnom             & 0.2.pnom     	& 0.2.pnom    & -15         & -5.12       \\
CPU Time                & 10.1 hrs         			& 38.3 hrs 			& 6.2 min 		& 2.8 s 			& 2.6 s    		\\\\

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure_4_Errors_Convergence_v2.pdf}
\caption{Error convergence rates of the five different algorithms on the coagulation model. The objective error is the mean over $\mathcal{T}$= 25 trials.
DOPS, DDS and SA have the steepest drop in error during first 300 function evaluations. Thereafter the error drop in DDS and SA remains nearly constant whereas DOPS continues to drops further.
At the end of 4000 function evaluations DOPS attains the lowest error. The next best estimate using DDS is nearly three times greater than the lowest error using DDS.
}\label{fig-convergence}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S1_B1_sims.pdf}
\caption{\textbf {(Data fits for Problem B1)} Pseudo-experimental data (red circles) vs. optimal solution obtained using DOPS (solid blue lines) for the 44 observed states. X axis: time [s]; Y axis: metabolite concentrations [mM].
}\label{fig-sims-b1}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S2_B4_sims.pdf}
\caption{\textbf {(Data fits for Problem B4)} Pseudo-experimental data (red x) vs. optimal solution obtained using DOPS (solid blue lines) for the 13 observed states. X axis: time [s]; Y axis: metabolite concentrations [mM].
}\label{fig-sims-b4}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./figs/Figure_S3_B1_B4_params_measuredstates.pdf}
\caption{ \textbf {(A)} Difference between nominal and optimal parameters for problem B1: Genome wide kinetic model of \textit{S.cerevisiae} with 1759 unknown parameters. \textbf {(B)} Difference between experimental (measured) data and data simulated with optimal parameters for problem B1: Genome wide kinetic model of \textit{S.cerevisiae} with 1759 unknown parameters. \textbf {(C)} Difference between nominal and optimal parameters for problem B4: Metabolic model of Chinese  Hamster Ovary Cells (CHO) cells with 117 parameters. \textbf {(D)} Difference between experimental (measured) data and data simulated with optimal parameters for problem B4: Metabolic model of Chinese  Hamster Ovary Cells (CHO) cells with 117 parameters.
}\label{fig-benchmark}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[trim = {0 5cm 0 5cm }, clip, width=1.00\textwidth]{./rachelfigs/TimeComparsion.pdf}
\caption{ Comparison of the runtime of the different optimization methods used for comparison with  $\mathcal{T}$ = 25 trials per method. All methods used take about the same amount of time to perform 4,000 function evaluations on the coagulation problem, as this problem is very stiff, so the majority of the time is spent solving the system of differential equations.
}\label{fig-time-comparsion}
\end{figure}

\begin{figure}%
    \centering
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/RecreateRebutalReviewer1_FigS4a} }}%
    \qquad
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/RecreateRebutalReviewer1_FigS4b} }}%
    \caption{Mean onvergence curves for different metaheuristics for (a) Ackley 300 dimensional and (b) Rastrigin 300 dimensional with $\mathcal{T}$ = 25 trials per method. DOPS not only finds a better solution than any other technique, it finds it with fewer function evaluations}%
    \label{fig-more-methods}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/CompareExperimentalDOPSToESSOnProblemB4} }}%
    \qquad
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/CompareExperimentalDOPSToESSOnCoag} }}%
    \caption{Mean convergence curves for DOPS and ESS for (a) CHO model (problem B4) (b) coagulation with $\mathcal{T}$ = 25 trials per method.}%
    \label{fig-compare-DOPS-ESS}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/DOPSDispersionCurvesOnb4} }}%
    \qquad
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/DOPSDispersionCurvesOnCoag} }}%
    \caption{Dispersion curves for DOPS on (a) CHO model (problem B4) (b) coagulation with $\mathcal{T}$ = 25 trials per problem .}%
    \label{fig-DOPS-Dispersion-Curves}%
\end{figure}

\begin{figure}%
    \centering
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/FigureS7a} }}%
    \qquad
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/FigureS7b} }}%
    \qquad
        \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/FigureS7c} }}%
    \qquad
    \subfloat[]{{\includegraphics[trim = {3cm 7cm 3cm 7cm }, clip,width=.45\textwidth]{./rachelfigs/FigureS7d} }}%
    \caption{Variability  analysis in best objective value for $\mathcal{T}$ = 25 trials. (a) Ackley  300 dimensional (b) Rastrigin 300 dimensional (c) CHO model (problem b4) (d) coagulation. }%
    \label{fig-DOPS-Dispersion-Curves}%
\end{figure}
